\usepackage{parskip}

\documentclass{table}
\title{Project Use Cases}

\begin{document}
	
	Use Cases
	UC1 - Open App
	User opens the app and is presented with a map of campus honed in on their current location as well as a search bar at the top to indicate where they would like to go.

	UC2 - Location Search
	User either types in the name of the location or selects it on the map by placing a “pin”. The user is then presented with routes to the destination if the destination exists.

	UC3 - User Input
	The user can add information that describes what he or she is interested in with regards to activities or pastime events so that points of interest can be highlighted to them as they walk through campus. 

	UC4 - User timetable
	The timetable can also be added by the user so that the route can automatically be determined based on his or her schedule.

	UC5 - Optimal Route and Traveling
	The user has requested a route to a destination and is presented with multiple options based on campus congestion. These route options will provide estimated time of arrival for each one allowing the user to make an informed decision.The optimal route will be shown and map changed based on whether the user is indoors or outdoors.

	UC6 - Activities
	User selects a route and the estimated number of steps is added to their user profile in a game like fashion leading to possible rewards awarded by third party members. 

	UC7 - User Based Augmented Reality 
	As the user travels along their route and passes certain landmarks they will be presented with certain information about these landmarks. For example if they pass the music department they will be given the option to see upcoming performances. This will be based on the interests that they have specified on their profiles. 

	UC8 - End Point
	Once the user reaches their destination navigation will stop until the user enters in a new location or the location is pulled from their timetable information.

\end{document}